Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Lack of management support

@@

\subsubsection{Challenges relating to leading the change}

In the beginning of the transformation the organization has realized the need to
change and is going towards the initial push.
In many cases the initiative to change came from management, but when presented
wrong the initiative becomes a mandate. Spayd summarizes this as:
``Organizations do not change merely because the boss says so, at least not in
the way that is intended'' [P49]. In that organization the introduction of CMM
was carried out consistently by a mandate, but the collaborative nature of agile
did not comply with such a mindset. A top down mandate may also dilute the
understanding of the reasons for starting the transformation, and further for
agile development overall [P2].

@@

Another issue that should be avoided is overenthusiasm towards agile methods.
In several cases there was mentionings about change leaders or teams becoming
agile zealots. For instance, Evans describes how some members of the agile
community were becoming too evangelic, which made people take sides for or
against agile development [12]. In another case team members started out with an
overly eager attitude, but when agile did not deliver improvements quickly the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

@@

\subsubsection{Challenges in managing the changing organization}

>>>>

Work in progress...

@@

\subsubsection{Tensions between management and development}

% In the beginning of the transformation the organization has realized the need
% to change and is going towards the initial push.
In many cases the initiative to change came from management, but when presented
wrong the initiative becomes a mandate. Spayd summarizes this as:
``Organizations do not change merely because the boss says so, at least not in
the way that is intended'' [P49]. In that organization the introduction of CMM
was carried out consistently by a mandate, but the collaborative nature of agile
did not comply with such a mindset. A top down mandate may also dilute the
understanding of the reasons for starting the transformation, and further for
agile development overall [P2].

@@

Another issue that should be avoided is overenthusiasm towards agile methods.
In several cases there was mentionings about change leaders or teams becoming
agile zealots. For instance, Evans describes how some members of the agile
community were becoming too evangelic, which made people take sides for or
against agile development [12]. In another case team members started out with an
overly eager attitude, but when agile did not deliver improvements the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

@@

The problem of tension between management and development may also be opposite.
In cases where the change was emerging bottom up the reluctancy to change was
not in the team members but management.
This caused that significant organizational change could not be raised above the
team level. For instance, Atlas describes how it would have required executive
support to integrate the product management office and separate quality
assurance groups in the agile process [P3]. In this case, when managers owning
projects with many teams were not involved it retrained agile development to
spread beyond team level. Further, if management does not speak out a goal
towards using agile, developers feel that the agile methods may be replaced by
something else at any time [P12].
Lack middle management support was seen as the most serious shortcoming by
Spayd [P49]. Middle management is in a position to undermine the entire
transformation, and may do so if they do not participate in, and thus
understand, the agile method [P49].
